On the Bit Complexity of Finding Points in Connected Components of a Smooth Real Hypersurface

### 2020-02-05 main.tex
sec 4

% packages 
\usepackage[ruled,vlined]{algorithm2e}
\usepackage{mathrsfs}
\usepackage{bm}
\usepackage{enumitem}
% new commands and shortcuts
\def\td{{\bf todo}}
\def\bs{\textit{\textbf{s}}}
\def\bz{\textit{\textbf{0}}}
\def\Lb{\textit{\textbf{L}}}
\def\Xb{\textit{\textbf{X}}}
\def\Lambdab{\bm{\Lambda}}
\def\Thetab{\bm{\Theta}}
\def\thetab{\bm{\vartheta}}
\def\mA{{\bm A}}
\def\fA{{\frak A}}
\def\xb{\textit{\textbf{x}}}
\def\fb{\textit{\textbf{f}}}
\def\ab{\textit{\textbf{a}}}
\def\pb{\textit{\textbf{p}}}
\def\ajb{\overline{a_j}}
\def\bjb{\overline{b_{j,l}}}
\def\pjb{\overline{P_{j}}}
\DeclareMathOperator{\GL}{GL}
\DeclareMathOperator{\htt}{ht}
\def\C{\mathbb{C}}
\def\pr{\mathbb{P}}
\def\vt{\vartheta}
\def\Q{\mathbb{Q}}
\def\R{\mathbb{R}}
\def\K{\mathbb{K}}
\def\rs{\mathscr{R}}
\def\P{\mathscr{P}}
\def\d{\delta}
\def\sing{ \textrm{sing}}
\def\codim{ \textrm{codim}}
\def\jac{ \textbf{jac}}
\def\exp{\textrm{exp}}
\def\grad{\textrm{grad}}
\def\rank{\textrm{rank}}
\def\reg{\textrm{reg}}
\def\jt{\widetilde{J}}
\def\At{\widetilde{A}}
\def\Yt{\widetilde{Y}}
\def\dtt{\widetilde{d}}
\def\kt{\widetilde{k}}
\def\dt{s}
\def\bI{\textbf{I}}
%% \def\dt{\widetilde{d}}
\def\Dt{\widetilde{D}}
\def\rk{\textrm{rank }}
\def\pa{\partial}
\def\D{\Delta}
\def\Z{\frak{Z}}
\newcommand{\ZZ}{{\mathbb{Z}}}
\newcommand{\softO}{{O^{\sim}}}
\def\I{\frak{I}}
\def\Is{\frak{I}^{\star}}
\def\A{\frak{A}}
\def\fp{\frak{P}}
\def\sp{\mathscr{P}}
\def\la{\langle}
\def\ra{\rangle}
% matrices 
\def\scrQ{\ensuremath{\mathscr{Q}}}
\def\bbm{\begin{bmatrix}}
\def\ebm{\end{bmatrix}}
%%
%% \BibTeX command to typeset BibTeX logo in the docs
\AtBeginDocument{%
  \providecommand\BibTeX{{%
    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}

@@

\section{Genericity properties}

@@

We will also work with changes of variables with ``generic entries''.
For this, we will introduce $n^2$ new indeterminates $(\frak
A_{i,j})_{1\le i,j \le n^2}$, we will let $\K$ be the field $\C(\frak
A_{i,j})_{1\le i,j \le n^2}$, and use the corresponding matrix $ \fA$
over $\K$. For $g$ as above, we will then define the polynomial 
$g^\fA:=g(\fA \Xb) \in \K[X_1,\dots,X_n]$.

@@

Sard's lemma states that the set of critical values of a smooth
function $\R^n \to \R^m$ has measure zero. One can give ``algebraic''
versions of it, for semi-algebraic mappings $\R^n \to \R^m$ as
in~\cite[Chapter~9]{bochnak1998real} or polynomial mappings $\C^n \to
\C^m$ as in~\cite[Chapter~3]{Mumford76}, for which the sets of
critical values are contained in strict semi-algebraic,
resp.\ algebraic sets in the codomain. Thom's weak transversality
lemma, as given for instance in~\cite{demazure2000bifurcations},
generalizes Sard's lemma. In this section, we consider a particular
case of this result (transversality to a point), and establish a
quantitative version of it; this will allow us to establish the first
item in property ${\bf H}_i$, as well as property ${\bf H}'_i$. Our
presentation is inspired by that in~\cite{TWT}.

@@

Recall that we work with changes of variables with ``generic entries'' of new indeterminants $(\frak
A_{i,j})_{1\le i,j \le n^2}$, and define the polynomial 
$f^\fA:=f(\fA \Xb)$. Note that $f^\A$ satisfies $\textbf{H}_i(1).$ Indeed, otherwise it could not be that that the Jacobian of $f^A,\frac{\pa f^A}{\pa X_{i+1}},\hdots,\frac{\pa f^A}{\pa X_n}$ has full rank at all $\xb \in V(f^A)$ for a generic $A \in \C^{n^2},$ which would contradict Popositon 3.1. The proof of this statement is routine and we omit details. We will rely on this
fact in Section 8.

@@

\subsection{Application: property $\textbf{H}_i(1)$}

@@

@@

\section{Property ${\bf H}_i(2)$ -- Noether position}

Fix $i \in \{1,\hdots,n\}$. Throughout this section, we will avoid writing $i$ where the context is clear. Let $\I^{\A}$ denote $\I(i,V^{\A}).$

We prove that there exists a hypersurface $\D_{3,i} \subset
\C^{n^2}$ such that if $\mA$ is not in $\D_{3,i}$, then $\mA$ is
invertible and satisfies $\textbf{H}_i(1)$ and $\textbf{H}_i(2)$.

Recall that we work with changes of variables with ``generic entries'' of new indeterminants $(\frak
A_{i,j})_{1\le i,j \le n^2}$, and define the polynomial 
$f^\fA:=f(\fA \Xb)$. Recall as well that $f^\A$ satisfies $\textbf{H}_i(1),$ as was stated at the end of Section 3.1. 
%
\subsection{Sketch of the proof}
%
Let $f \in \ZZ[X_1,\hdots,X_n]$ have total degree $d$ with $V(f) \subset \C^n$ smooth. Recall $\textbf{H}_i(2):$ \textit{$W(\pi_i,V(f))$ is either empty or in Noether position for
  $\pi_{i-1}$}, which is equivalent to having the extension  
\[
\C[\textbf{X}_{\leq i-1}]\rightarrow\C[\textbf{X}]/\frak{I}(\pi_i,V)
\]
injective and  integral.
%
\begin{theorem}
There exists a hypersurface $\Delta_3 \subset \C^{n^2}$ of degree at most $\td$ with the property that, if $A \in \C^{n^2} - \Delta_3$ then, for each $i \in\{1,\hdots,n\}, \mA$ is
invertible and satisfies $\textbf{H}_i(1)$ and $\textbf{H}_i(2)$.
\end{theorem}
%
\begin{proposition} 
The ring extension \[\mathbb{Q}(\frak{A})[\textbf{X}_{\leq i-1}]\rightarrow\mathbb{Q}(\frak{A})[\textbf{X}]/\I^{\A}\] is integral.
\end{proposition}
%
\begin{proof}
Let $(\frak{P}_l)_{l \leq L}$ be the prime components of the radical ideal $\I^\A$. By \cite[Proposition 1]{EMP}, 
\[
\mathbb{Q}(\frak{A})[\Xb_{\leq i-1}]\rightarrow\mathbb{Q}(\frak{A})[\Xb]/\fp_l^{\A}
\] 
is integral. Therefore polynomials $p_{l,j}\in\mathbb{Q}(\frak{A})[\Xb_{\leq i-1}][T]$ exist, monic in $T$, with $p_{l,j}(X_j)\in \frak{P}_l$ for each $j\in \{i,\hdots,n\}.$ Thence, 
%
\begin{align*}
&P_{j}(X_j) := \prod_l p_{l,j}(X_j)\in\I^\A, 
\end{align*}
%
for each $j \in \{i,\hdots,n\},$ and therefore 
\[
\mathbb{Q}(\frak{A})[\Xb_{\leq i-1}]\rightarrow\mathbb{Q}(\frak{A})[\Xb]/\I^{\A}
\] 
is integral.
\end{proof}
%
Let $P_{j} \in \mathbb{Q}(\frak{A})[\Xb_{\leq i-1}][T]$ be as in the proof of Proposition 4.2. Since $P_{j}(X_j) \in\I^{\A}= \langle f^\A,\frac{\partial f^\A}{\partial X_{i+1}},\hdots,\frac{\partial f^\A}{\partial X_n} \rangle,$
 we can write
\[
P_{j}(X_j) = a_j f^{\A} + \sum_{l=1}^{n-i}b_{j,l} \frac{\partial f^\A}{\partial X_{i+l}}, ~a_j,b_{j,l} \in \mathbb{Q}(\A)[\textbf{X}].
\]
For each $P_j,$ there exists a Zariski open set $\Gamma_j \subset \C^{n^2}$ such that if $\mA \in \Gamma_j$,
then $\mA$ cancels none of the denominators of $a_{j}$ or $b_{j,l}$. Define $h_j \in \Q[\A]$ to be the product of the denominators of the coefficients of $a_j$ and $b_{j,l}$. Hence, if $\mA \in \C^{n^2}-V(h_j)$ then $\mA$ cancels none of the denominators of $a_{j}$ or $b_{j,l},$ which are providing the integral dependence relation. Now we define 
\[
\Xi_i := \bigcup_{j=i}^n V(h_j) =V\left(\prod_{j=i}^n h_j \right), 
\]
and we obtain a bound on the degree of $\Xi_i$ by observing that
\[
\deg \Xi_i \leq \sum_{j=i}^n \deg h_j.
\]
Hence, if $\mA\in \Q^{n^2}-\Xi_i$ then
\[
P_j(X_j) \in \I^A,  
\]
for each $j \in \{i,\hdots,n\},$ and therefore the extension 
\[
\mathbb{C}[{\Xb}_{\leq i-1}]\rightarrow\mathbb{C}[\Xb]/\I(\pi_i,V^{\mA})
\]
is integral. We can obtain bounds for $h_j$ by applying an effective Nullstellensatz theorem. However, the theorem requires $P_{j}$ to be a polynomial. We can obtain a polynomial from $P_{j}$ by clearing denominators. We can multiply $P_{j}$ by the least common multiple of its denominators, which we will denote by $d_j \in \Q[\A]$. Put 
\[
\overline{P_{j}} := d_jP_{j}\in \Q[\A][\Xb],
\]
and note that $\pjb(X_j) \in \I^{\A}$ with 
\[
\pjb(X_j) = \ajb f^{\A} + \sum_{l=1}^{n-i}\bjb \frac{\partial f^\A}{\partial X_{i+l}}, ~\ajb,\bjb \in \mathbb{Q}[\A][\textbf{X}].
\]
%
\begin{proposition} 
$\deg \pjb\leq (d+1)^{n-i+1}.$ 
\end{proposition} 
%
\begin{proof}
\textbf{Eric and Mark}: I am unsure of how to do this part correctly, so I will assume 
\[
\deg \pjb\leq \Dt_j.
\]
Let $\Is \subset \Q[\A,\Xb]$ be the extension of $\I^{\A}$ in  $\Q[\A,\Xb],$ and consider the finite field extension
%
\begin{align*}
    \Q(\A,\Xb_{i-1}) &\rightarrow \Q(\A,\Xb_{i-1})[X_i,\hdots,X_n]/\Is.
\end{align*}
%
The minimal polynomial of the linear mapping defined by multiplication by $X_j$ in $\Q(\A,\Xb_{i-1})$ is \textbf{almost}(?) equal to $\pjb$ (the leading coefficient of $\pjb$ is $d_j$). It therefore follows by \cite[Proposition 1]{CGR} that
%
\begin{align*}
&\deg \pjb \leq (d+1)^{n-i+1}.&(2d)^{n-i+1}\textrm{?} 
\end{align*}
%
\end{proof}
%
Note that 
\[
\deg d_j \leq \deg \pjb \leq \Dt_j.
\]
%
\subsection{Applying the effective Nullstellensatz}
%
To apply the effective Nullstellensatz theorem, we first need to determine degree bounds, separately in $\Xb$ and $\A,$ of the polynomials in the membership relationship. We have
\[
\deg_{\Xb}\left\{ 
f^\A,\frac{\partial f^\A}{\partial X_{i+1}},\hdots,\frac{\partial f^\A}{\partial X_n}
\right\}\leq d,
\]
\[
\deg_{\A}  
\left\{ 
f^\A,\frac{\partial f^\A}{\partial X_{i+1}},\hdots,\frac{\partial f^\A}{\partial X_n}
\right\} \leq d,
\]
\[
\deg_{\Xb,T}(1-T\pjb) \leq \Dt_j +1 
\]
and
\[
\deg_{\A}(1-T\pjb) \leq \Dt_j.
\]
For each $j \in \{i,\hdots,n\},$ by \cite[Theorem 0.5]{EN}, there exists $\alpha_j \in \mathbb{Q}[\A]\setminus\{0\}$ with 
%
\begin{align*}
\alpha_j = \sum_{l=1}^{n-i+1} A_{j,l}(\A,\Xb,T)g_l + B_j(\A,\Xb,T)(1-\pjb T), \\ g_l \in 
\left\{ 
f^\A,\frac{\partial f^\A}{\partial X_{i+1}},\hdots,\frac{\partial f^\A}{\partial X_n}
\right\},~ A_{j,l},B_j \in \mathbb{Q}[\A][\Xb][T],
\end{align*}
%
and with the degree of $\alpha_j$ upper bounded by
%
\begin{align*}
    &\left(\prod_{k=1}^{n-i+1} d\right)\Dt_j 
    + (n-i+1)\left(\Dt_j+1\right)\left(\prod_{k=1}^{n-i}d \right)d\\
    = &\left(d^{n-i+1}\right)\Dt_j+
    (n-i+1)\left(\Dt_j+1\right)\left(d^{n-i+1} \right)\\
    &\leq d^{n}\Dt_j + n\left(\Dt_j+1\right)d^{n}\\
    &=d^n\left(\Dt_j + n\left(\Dt_j+1\right) \right).
\end{align*}
%
Now we will show that $\alpha_j$ is the only remaining denominator whose degree we need to bound. Substitute $T \leftarrow 1/\pjb$ so that 
\[
\alpha_j = \sum_{l=1}^{n-i+1} A_{j,l}(\A,\Xb,1/\pjb)g_l + 0
\]
and
%
\begin{align*}
A_{j,l}(\A,\Xb,1/\pjb) 
&= \sum_{i=1}^{n_l} A_{j,l,i}(\A,\Xb,1/\pjb)\\
&= \sum_{i=1}^{n_l} \left(\frac{1}{P_j^{k_i}}\right)\At_{j,l,i}(\A,\Xb), ~k_i \in \mathbb{Z}.
\end{align*}
%
Let $K := \max\{k_l\}$ so that 
%
\begin{align*}
    \pjb^K \alpha_j &= \pjb^K\left(\sum_{l=1}^{n-i+1} A_{j,l}(\A,\Xb,1/\pjb)g_l\right)\\
    &= \sum_{l=1}^{n-i+1}\left( \sum_{i=1}^{n_l}\left(\pjb^{K-k_{i}}\right)\At_{j,l,i}(\A,\Xb) \right)g_l \in \Q[\A][\Xb].
\end{align*}
%
which shows that $\alpha_j$ is the only remaining denominator whose degree we need to bound other than $d_j$. Note as well that
\[
\pjb^K \in \I^{\A}.
\]
Therefore 
%
\begin{align*}
\deg h_j &\leq \left(\deg \alpha_j\right)\left(\deg d_j\right)\\
    &\leq \left(d^n\left(\Dt_j + n\left(\Dt_j+1\right) \right)\right)\Dt_j\\
    &=d^n\Dt_j\left(\Dt_j + n\left(\Dt_j+1\right) \right).
\end{align*}
%
\subsection{Proof of Theorem 7.1}
%
Now we obtain
%
\begin{align*}
    \deg \Xi_i 
    &\leq \sum_{j=i}^n \deg h_j\\
    &\leq  \sum_{j=i}^n \left( d^n\Dt_j\left(\Dt_j + n\left(\Dt_j+1\right) \right) \right) \\
    &=  (n-i+1)\left( d^n\Dt_j\left(\Dt_j + n\left(\Dt_j+1\right) \right) \right)\\
    &\leq  n d^n\Dt_j\left(\Dt_j + n\left(\Dt_j+1\right) \right) .
\end{align*}
%
And therefore,  
%
\begin{align*}
    \deg& \Delta_3 \leq \sum_{i=1}^n \deg \Xi_i\\
    &\leq n^2 d^n\Dt_j\left(\Dt_j + n\left(\Dt_j+1\right) \right),
\end{align*}
%
where if $A \in \C^{n^2} - \Delta_3$ then, for each $i \in \{1,\hdots,n\},$ the extension 
\[
\C[\textbf{X}_{\leq i-1}]\rightarrow\C[\textbf{X}]/\frak{I}(\pi_i,V^A)
\]

>>>>

% packages 
\usepackage[ruled,vlined]{algorithm2e}
\usepackage{mathrsfs}
\usepackage{bm}
\usepackage{enumitem}
% new commands and shortcuts
\def\td{{\bf todo}}
\def\bs{\textit{\textbf{s}}}
\def\bz{\textit{\textbf{0}}}
\def\Lb{\textit{\textbf{L}}}
\def\Xb{\textit{\textbf{X}}}
\def\Lambdab{\bm{\Lambda}}
\def\Thetab{\bm{\Theta}}
\def\thetab{\bm{\vartheta}}
\def\mA{{\bm A}}
\def\fA{{\frak A}}
\def\xb{\textit{\textbf{x}}}
\def\fb{\textit{\textbf{f}}}
\def\ab{\textit{\textbf{a}}}
\def\pb{\textit{\textbf{p}}}
\def\ajb{\overline{a_j}}
\def\bjb{\overline{b_{j,l}}}
\def\pjb{\overline{P_{j}}}
\DeclareMathOperator{\GL}{GL}
\DeclareMathOperator{\htt}{ht}
\def\C{\mathbb{C}}
\def\pr{\mathbb{P}}
\def\vt{\vartheta}
\def\Q{\mathbb{Q}}
\def\R{\mathbb{R}}
\def\K{\mathbb{K}}
\def\rs{\mathscr{R}}
\def\P{\mathscr{P}}
\def\d{\delta}
\def\sing{ \textrm{sing}}
\def\codim{ \textrm{codim}}
\def\jac{ \textbf{jac}}
\def\exp{\textrm{exp}}
\def\grad{\textrm{grad}}
\def\rank{\textrm{rank}}
\def\reg{\textrm{reg}}
\def\jt{\widetilde{J}}
\def\At{\widetilde{A}}
\def\Yt{\widetilde{Y}}
\def\kt{\widetilde{k}}
\def\dt{s}
\def\bI{\textbf{I}}
%% \def\dt{\widetilde{d}}
\def\Dt{\widetilde{D}}
\def\rk{\textrm{rank }}
\def\pa{\partial}
\def\D{\Delta}
\def\Z{\frak{Z}}
\newcommand{\ZZ}{{\mathbb{Z}}}
\newcommand{\softO}{{O^{\sim}}}
\def\I{\frak{I}}
\def\Is{\frak{I}^{\star}}
\def\A{\frak{A}}
\def\fp{\frak{P}}
\def\sp{\mathscr{P}}
\def\la{\langle}
\def\ra{\rangle}
% matrices 
\def\scrQ{\ensuremath{\mathscr{Q}}}
\def\bbm{\begin{bmatrix}}
\def\ebm{\end{bmatrix}}
%%
%% \BibTeX command to typeset BibTeX logo in the docs
\AtBeginDocument{%
  \providecommand\BibTeX{{%
    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}

@@

\section{Genericity properties}\label{sec:gen}

@@

It will on occasion be useful to work with change of variables with
``generic'' entries. For this, we will introduce $n^2$ new indeterminates
$(\frak A_{j,k})_{1\le j,k \le n^2}$, we will let $\K$ be the field
$\C(\frak A_{i,j})$, and use the corresponding
matrix $\A$ over $\K$. For $f$ as above, we will then define the
polynomial $f^\A:=f(\A \Xb) \in \K[X_1,\dots,X_n]$.

@@

Sard's lemma states that the set of critical values of a smooth
function $\R^n \to \R^m$ has measure zero. One can give ``algebraic''
versions of it, for semi-algebraic mappings $\R^n \to \R^m$ as
in~\cite[Chapter~9]{bochnak1998real}, or polynomial mappings $\C^n \to
\C^m$ as in~\cite[Chapter~3]{Mumford76}, for which the sets of
critical values are contained in strict semi-algebraic,
resp.\ algebraic sets in the codomain. Thom's weak transversality
lemma, as given for instance in~\cite{demazure2000bifurcations},
generalizes Sard's lemma. In this section, we consider a particular
case of this result (transversality to a point), and establish a
quantitative version of it; this will allow us to establish the first
item in property ${\bf H}_i$, as well as property ${\bf H}'_i$. Our
presentation is inspired by that in~\cite{TWT}.

@@

@@

\subsection{Application: property $\textbf{H}_i(1)$}\label{ssec:Hi1}

@@

In Section~\ref{sec:Hi2}, we will need the following alternative form
of this result: if we consider $f^\A \in \C(\frak
A_{j,k})[X_1,\dots,X_n]$ as defined Section~\ref{sec:gen}, this
polynomial satisfies the rank property $\textbf{H}_i(1)$.

@@

\section{Property ${\bf H}_i(2)$ -- Noether position}\label{sec:Hi2}

Throughout this section, $f$ and $i \in \{1,\hdots,n\}$ are fixed. We
prove that there exists a hypersurface $\D_{3,i} \subset \C^{n\times
  n}$ of degree at most \td{} such that if $\mA$ is not in $\D_{3,i}$,
then $\mA$ is invertible and satisfies both conditions in
$\textbf{H}_i$.

Consider again the $n\times n$ matrix of indeterminates
$\A=(\A_{j,k})_{1 \le j,k \le n}$ and the field $\C(\A)$,
and define $f^{\A} \in \C(\A)[X_1,\dots,X_n]$.  Since $i$ is fixed, to
simplify notation, let $\I^\A$ denote the following polynomials in
$\C(\A)[X_1,\dots,X_n]$:
$$\I(\pi_i,f^\A)= \big (f^\A, {\pa f^\A}/{\pa X_{i+1}},\dots,{\pa
  f^\A}/{\pa X_n}) \big ),$$ and let $W^\A$ denote their zero-set,
that is, $W(\pi_i,V(f^\A)).$ In Section~\ref{ssec:Hi1}, we saw that
$f^\A$ satisfies $\textbf{H}_i(1)$, so that $\I^\A$ defines a
radical ideal, and $W^\A$ is equidimensional of dimension $i-1$. We
now point out that $f^\A$ also satisfies $\textbf{H}_i(2)$.

\begin{lemma} 
 The extension $\C(\A)[X_1,\dots,X_{i-1}]\rightarrow
 \C(\A)[X_1,\dots,X_n]/\I^{\A}$ is integral.
\end{lemma}
\begin{proof}
  Let $(\fp_\ell)_{1 \le \ell \leq L}$ be the prime components of
  the radical ideal $\I^\A$. By \cite[Proposition 1]{EMP}, for all
  $\ell$,
  \[
    \C(\A)[X_1,\dots,X_{i-1}]\rightarrow\C(\A)[X_1,\dots,X_n]/\fp_\ell
  \] 
  is integral. Therefore polynomials
  $q_{\ell,j}\in\C(\A)[X_1,\dots,X_{i-1},X_j]$ exist, all monic in
  $X_j$, with $q_{\ell,j}(X_j)\in \fp_\ell$ for each $j$ in
  $\{i,\hdots,n\}.$ Thence, $ Q_{j} := \prod_{1 \le \ell\le L}
  q_{\ell,j}$ is monic in $X_j$ and satisfies $ Q_{j} \in \I^\A$, for
  each $j \in \{i,\hdots,n\}.$ This proves our claim.
\end{proof}

\noindent
If $P$ is any polynomial in $\C(\frak A)[X_1,\dots,X_n]$, we will let
$D \in \C[\frak A]$ be the minimal common denominator of all its
coefficients, and we will write $\overline P := D P$, so that
$\overline P$ is in $\C[\A,X_1,\dots,X_{i-1},X_n]$.

\begin{lemma} 
  For $j=i,\dots,n$, there exists $P_j$ in $
  \C(\A)[X_1,\dots,X_{i-1},X_j]$, monic in $X_j$, with $\pjb$ in
  $\I^\A$, and such that $\deg(\pjb)\leq (2d)^{n-i+1}.$
\end{lemma} 
\begin{proof}
  We let $\frak L^\A$ denote the extension of $\I^\A$ given by $\frak
  L^\A:=\I^\A\cdot \C(\frak A, X_1,\dots,X_{i-1})[X_i,\dots,X_n]$. Then,
  \begin{equation}\label{eq:1}
    \C(\frak A, X_1,\dots,X_{i-1}) \to \C(\frak A,
    X_1,\dots,X_{i-1})[X_i,\dots,X_n]/\frak L^\A
  \end{equation}
  is an algebraic extension. On the other hand, 
  the previous lemma states that 
  \begin{equation}\label{eq:2}
    \C(\A)[X_1,\dots,X_{i-1}]\rightarrow
    \C(\A)[X_1,\dots,X_n]/\I^{\A}  
  \end{equation}
  is integral; from this, Proposition~3.3.1 in~\cite{GiHeSa93} implies
  that it is actually a free module. Any basis of the latter is also a
  basis of~\eqref{eq:1}; as a consequence, for $j$ in $i,\dots,n$, the
  characteristic polynomials of $X_j$ in~\eqref{eq:1} or~\eqref{eq:2}
  are the same. Let $P_j$ be the minimal polynomial of $X_j$
  in~\eqref{eq:1}. The previous discussion implies that the
  characteristic polynomial $\chi_j$ of $X_j$ in~\eqref{eq:1}, and
  thus also $P_j$, are in $\C(\A)[X_1,\dots,X_{i-1},X_j]$ and monic in
  $X_j$.

  By definition, $\chi_{j}$ is in $\frak I^\A$ and since there exists
  an integer $k$ such that $\chi_j$ divides $P_j{}^k$ in
  $\C(\A)[X_1,\dots,X_{i-1}][X_j]$, $P_j{}^k$ is in $\frak
  I^\A$. Since the latter ideal is radical, we conclude that $P_{j}$
  is in $\frak I^\A$. This implies that $\pjb$ is in $\frak I^\A$ as
  well.

  Now, consider the polynomials $f^\A, {\pa f^\A}/{\pa
    X_{i+1}}, \dots, {\pa f^\A}/{\pa X_n}$ in $\C[\A,X_1,\dots,X_n]$,
  let $\frak W$ be their zero-set, and let $\deg(\frak W)$ be its
  degree, in the sense of~\cite{H}. Proposition~1 in~\cite{CGR}
  implies that $\pjb$ has degree at most $\deg(\frak W)$. Since all
  polynomials defining $\frak W$, seen in $\C[\A,X_1,\dots,X_n]$, have
  degree at most $2d$, the B\'ezout inequality of~\cite{H} gives
  $\deg(\pjb) \le (2d)^{n-i+1}$.
\end{proof}

%% \[
%% \C[\textbf{X}_{\leq i-1}]\rightarrow\C[\textbf{X}]/\frak{I}(\pi_i,V)
%% \]
%% injective and  integral.

%%  Since $P_{j}(X_j) \in\I^{\A}= \langle
%% f^\A,\frac{\partial f^\A}{\partial X_{i+1}},\hdots,\frac{\partial
%%   f^\A}{\partial X_n} \rangle,$ we can write
%% \[
%% P_{j}(X_j) = a_j f^{\A} + \sum_{l=1}^{n-i}b_{j,l} \frac{\partial f^\A}{\partial X_{i+l}}, ~a_j,b_{j,l} \in \mathbb{Q}(\A)[\textbf{X}].
%% \]
%% For each $P_j,$ there exists a Zariski open set $\Gamma_j \subset
%% \C^{n^2}$ such that if $A \in \Gamma_j$, then $A$ cancels none of the
%% denominators of $a_{j}$ or $b_{j,l}$. Define $h_j \in \Q[\A]$ to be
%% the product of the denominators of the coefficients of $a_j$ and
%% $b_{j,l}$. Hence, if $A \in \Q^{n^2}-V(h_j)$ then $A$ cancels none of
%% the denominators of $a_{j}$ or $b_{j,l},$ which are providing the
%% integral dependence relation. Now we define
%% \[
%% \Xi_i := \bigcup_{j=i}^n V(h_j) =V\left(\prod_{j=i}^n h_j \right), 
%% \]
%% and we obtain a bound on the degree of $\Xi_i$ by observing that
%% \[
%% \deg \Xi_i \leq \sum_{j=i}^n \deg h_j.
%% \]
%% Hence, if $A\in \Q^{n^2}-\Xi_i$ then
%% \[
%% P_j(X_j) \in \I^A,  
%% \]
%% for each $j \in \{i,\hdots,n\},$ and therefore the extension 
%% \[
%% \mathbb{C}[{\Xb}_{\leq i-1}]\rightarrow\mathbb{C}[\Xb]/\I(\pi_i,V^{A})
%% \]
%% is integral. We can obtain bounds for $h_j$ by applying an effective
%% Nullstellensatz theorem.

%% %
%% Note that 
%% \[
%% \deg d_j \leq \deg \pjb \leq \Dt_j.
%% \]
%% %
%% \subsection{Applying the effective Nullstellensatz}
%% %

To apply the effective Nullstellensatz theorem, we first need to
determine degree bounds, separately in $\Xb$ and $\A,$ of the
polynomials in the membership relationship. We have
\[
\deg_{\Xb}\left\{ 
f^\A,\frac{\partial f^\A}{\partial X_{i+1}},\hdots,\frac{\partial f^\A}{\partial X_n}
\right\}\leq D,
\]
\[
\deg_{\A}  
\left\{ 
f^\A,\frac{\partial f^\A}{\partial X_{i+1}},\hdots,\frac{\partial f^\A}{\partial X_n}
\right\} \leq D,
\]
\[
\deg_{\Xb,T}(1-T\pjb) \leq \Dt_j +1 
\]
and
\[
\deg_{\A}(1-T\pjb) \leq \Dt_j.
\]
For each $j \in \{i,\hdots,n\},$ by \cite[Theorem 0.5]{EN}, there exists $\alpha_j \in \mathbb{Q}[\A]\setminus\{0\}$ with 
%
\begin{align*}
\alpha_j = \sum_{l=1}^{n-i+1} A_{j,l}(\A,\Xb,T)g_l + B_j(\A,\Xb,T)(1-\pjb T), \\ g_l \in 
\left\{ 
f^\A,\frac{\partial f^\A}{\partial X_{i+1}},\hdots,\frac{\partial f^\A}{\partial X_n}
\right\},~ A_{j,l},B_j \in \mathbb{Q}[\A][\Xb][T],
\end{align*}
%
and with the degree of $\alpha_j$ upper bounded by
%
\begin{align*}
    &\left(\prod_{k=1}^{n-i+1} D\right)\Dt_j 
    + (n-i+1)\left(\Dt_j+1\right)\left(\prod_{k=1}^{n-i}D \right)D\\
    = &\left(D^{n-i+1}\right)\Dt_j+
    (n-i+1)\left(\Dt_j+1\right)\left(D^{n-i+1} \right)\\
    &\leq D^{n}\Dt_j + n\left(\Dt_j+1\right)D^{n}\\
    &=D^n\left(\Dt_j + n\left(\Dt_j+1\right) \right).
\end{align*}
%
Now we will show that $\alpha_j$ is the only remaining denominator whose degree we need to bound. Substitute $T \leftarrow 1/\pjb$ so that 
\[
\alpha_j = \sum_{l=1}^{n-i+1} A_{j,l}(\A,\Xb,1/\pjb)g_l + 0
\]
and
%
\begin{align*}
A_{j,l}(\A,\Xb,1/\pjb) 
&= \sum_{i=1}^{n_l} A_{j,l,i}(\A,\Xb,1/\pjb)\\
&= \sum_{i=1}^{n_l} \left(\frac{1}{P_j^{k_i}}\right)\At_{j,l,i}(\A,\Xb), ~k_i \in \mathbb{Z}.
\end{align*}
%
Let $K := \max\{k_l\}$ so that 
%
\begin{align*}
    \pjb^K \alpha_j &= \pjb^K\left(\sum_{l=1}^{n-i+1} A_{j,l}(\A,\Xb,1/\pjb)g_l\right)\\
    &= \sum_{l=1}^{n-i+1}\left( \sum_{i=1}^{n_l}\left(\pjb^{K-k_{i}}\right)\At_{j,l,i}(\A,\Xb) \right)g_l \in \Q[\A][\Xb].
\end{align*}
%
which shows that $\alpha_j$ is the only remaining denominator whose degree we need to bound other than $d_j$. Note as well that
\[
\pjb^K \in \I^{\A}.
\]
Therefore 
%
\begin{align*}
\deg h_j &\leq \left(\deg \alpha_j\right)\left(\deg d_j\right)\\
    &\leq \left(D^n\left(\Dt_j + n\left(\Dt_j+1\right) \right)\right)\Dt_j\\
    &=D^n\Dt_j\left(\Dt_j + n\left(\Dt_j+1\right) \right).
\end{align*}
%
\subsection{Proof of Theorem 7.1}
%
Now we obtain
%
\begin{align*}
    \deg \Xi_i 
    &\leq \sum_{j=i}^n \deg h_j\\
    &\leq  \sum_{j=i}^n \left( D^n\Dt_j\left(\Dt_j + n\left(\Dt_j+1\right) \right) \right) \\
    &=  (n-i+1)\left( D^n\Dt_j\left(\Dt_j + n\left(\Dt_j+1\right) \right) \right)\\
    &\leq  n D^n\Dt_j\left(\Dt_j + n\left(\Dt_j+1\right) \right) .
\end{align*}
%
And therefore,  
%
\begin{align*}
    \deg& \Delta_3 \leq \sum_{i=1}^n \deg \Xi_i\\
    &\leq n^2 D^n\Dt_j\left(\Dt_j + n\left(\Dt_j+1\right) \right),
\end{align*}
%
where if $A \in \C^{n^2} - \Delta_3$ then, for each $i \in \{1,\hdots,n\},$ the extension 
\[
\C[\textbf{X}_{\leq i-1}]\rightarrow\C[\textbf{X}]/\frak{I}(\pi_i,V^A)
\]
